---
title: "Tidymodels workflow example - fraud prediction"
author: "Alex Farach"
date: "4/01/2021"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  cache = TRUE,
  cache.lazy = TRUE,
  warning = FALSE,
  message = FALSE,
  dpi = 180,
  fig.width = 8,
  fig.height = 5,
  echo = TRUE
  )

library(tidyverse)
theme_set(theme_minimal())
```

# Typical steps in a machine learning project ----------------------------------
1. Get the data
2. Explore the data
  - Study attributes
    - name
    - types 
    - missing values
    - noisiness (stochastic, outliers, etc)
    - Usefulness
    - Distributions (uniform, logarithmic, etc.)
  - Identify the dependent variable
  - Visualize the data
  - Review correlations
3. Prep the data
  - Clean-up
    - Fix or remove outliers
    - Fill in missing values or drop them.
  - Feature selection (maybe). Drop features that provide no useful info.
  - Feature engineering (maybe). Bucketing continuous variables, add 
    transformations (log, sqrts, etc.). Create new features like recency if
    dealing with time features.
  - Feature scaling (maybe). Normalize/standardize
4. Shortlist promising models
  - Train a bunch of quick and dirty models from different categories (e.g.
    linear, naive Bayes, SVM, random forest, neural net, etc.)
  - Measure and compare performance (use validation folds)
  - Analyze results
    - Significant variables
    - Errors
  - Quick round of feature selection and engineering.
  - Repeat above steps a couple of times.
  - Pick best model/s
5. Fine-tuning
  - Hyperparameter tuning using cross-validation
  - Ensemble methods (maybe)
  - Once confident about the final model, measure performance on test set.
6. Present results
7. Deploy model

In the example that follows I slowly add different elements of this whole list
in order to present the tidymodels machine learning approach in a more 
digestible form.

I will introduce concepts one by one and slowly build on each topic. 
Eventually, most everything above will be covered. This is to say what follows
is not the proper way to build a machine learning model - it's the way I find 
it easiest to learn about tidymodels and machine learning pipelines generally.

# Tidymodels approach 
## Get the data

The following table comes from the kaggle dataset: 
  https://www.kaggle.com/ntnu-testimon/paysim1
```{r}
# Import the data
fraud_data <- read_csv("./fraud/example_data/fraud_example.csv")
```

## Explore the data
```{r}
# Look at counts
fraud_data %>%
  group_by(isFraud) %>%
  summarise(
    n = n()
  ) %>%
  ungroup()

# Get percentages
fraud_data %>%
  count(isFraud) %>%
  mutate(per_n = scales::percent(n/sum(n), accuracy = 0.01))

# Create visual to explore variables
# set.seed(123)
# fraud_data %>%
#   sample_frac(0.03) %>%
#   select_if(is.numeric) %>%
#   GGally::ggscatmat(
#     columns = 1:6, 
#     color = "isFraud", 
#     alpha = 0.75,  
#     corMethod = "spearman"
#     ) +
#   ggsci::scale_color_jco() +
#   # ggpubr::theme_pubclean() +
#   # theme(
#   #   strip.background = element_blank(),
#   #   legend.position = "bottom",
#   #   legend.key = element_blank()
#   #   ) +
#   labs(
#     title = "Scatterplot matrix for fraud data numeric variables")
```

## Clean the data
```{r}
library(tidymodels)

set.seed(123)
# Clean data a bit
fraud_model_data <-
  fraud_data %>%
  select(
    isFraud, step, type, amount, oldbalanceOrg, newbalanceOrig, oldbalanceDest,
    newbalanceDest
  ) %>%
  mutate(
    isFraud = as.factor(if_else(isFraud == 0, "No", "Yes"))
  ) %>%
  mutate_if(is.character, as.factor) %>%
  sample_frac(0.03)

# Get percentages
fraud_model_data %>%
  count(isFraud) %>%
  mutate(per_n = scales::percent(n/sum(n), accuracy = 0.01))
```

## Create split, train, and test datasets

Here we are just creating a training and testing split. If you wanted to you
could split the training data further to get a validation set using the `mc_cv()`
function in the `rsample` package. This is a good practice but for the sake of 
simplicity I am omitting here.

It's also a good practice to split the data earlier so that steps taken in the
cleaning part of the machine learning process could be replicated in a ML
pipeline.

```{r}
# Set seed for reproducibility
set.seed(123)

# Create initial split
fraud_split <- initial_split(fraud_model_data, prop = 0.75, strata = isFraud)

# Assign the trainging set
fraud_train <- training(fraud_split)

# Assign the test set
fraud_test <- testing(fraud_split)

# Print out the size of training and testing sets
print(paste("Size of training data:", nrow(fraud_train)))
print(paste("Size of testing data:", nrow(fraud_test)))
```

# Modeling V1
Ideally you would want to use more than 2 models but here I will just present
2 for the sake of simplicity: a logistic model and a decision tree model.

If you would like to see all the models in Tidymodels you can do so by going to
this link: https://www.tidymodels.org/find/parsnip/

## Specify the model - simple logistic regression
```{r specify_lg_simple}
# Specify a logistic regression model
logistic_model <- logistic_reg() %>% 
  # Set the engine
  set_engine('glm') %>% 
  # Set the mode
  set_mode('classification')

# Print the model specification
logistic_model
```

## Fit the model to the training data
```{r fit_lg_simple}
# Fit to training data
logistic_fit <- logistic_model %>% 
  fit(isFraud ~ ., data = fraud_train)

# Print model fit object
logistic_fit
```

## Combine test dataset results
```{r combine_lg_simple_pred}
# Predict outcome categories
class_preds <- predict(logistic_fit, new_data = fraud_test,
                       type = 'class')

# Obtain estimated probabilities for each outcome value
prob_preds <- predict(logistic_fit, new_data = fraud_test,
                       type = 'prob')

# Combine test set results
fraud_results <- fraud_test %>% 
  select(isFraud) %>% 
  bind_cols(class_preds, prob_preds)

# View results tibble
fraud_results
```

## Evaluate performance
```{r evaluate_lg_simple}
# Create custom metric set to evaluate performance.
custom_metrics <- metric_set(accuracy, sens, spec)

# Print out the custom metrics results
custom_metrics(fraud_results, truth = isFraud, estimate = .pred_class)

# Here are all the available metrics
conf_mat(fraud_results, truth = isFraud, estimate = .pred_class) %>%
  summary()
```

## Visual evaluation - confusion matrix, ROC curve and area under ROC curve
```{r eval_lg_simple_viz}
# Create confusion matrix to see TP, FP, TN, and FN results
fraud_results %>%
  conf_mat(truth = isFraud, estimate = .pred_class) %>%
  autoplot('heatmap')

# Plot roc_curve
fraud_results %>%
  roc_curve(truth = isFraud, estimate = .pred_No) %>%
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )

# Print out the AUC of the ROC curve
roc_auc(fraud_results, truth = isFraud, .pred_No)
```

## Complete the model training process

Our approach thus far has been really simple. We only used a single training 
set. Later on I'll show you how to use validation folds and I mentioned the use 
of a validation set above which would add some complications to these first 
model training steps. If we took that route we would want to do one last fit of 
the model on all the training data - not the folded and train/validation split 
data.

```{r lg_simple_wf}
# Train model with last fit
fraud_last_fit <- logistic_model %>%
  last_fit(isFraud ~ ., split = fraud_split)

# Collect predictions
last_fit_results <- fraud_last_fit %>%
  collect_predictions()

# Custom metrics function
last_fit_metrics <- metric_set(accuracy, sens,
                               spec, roc_auc)

# Calculate metrics
last_fit_metrics(last_fit_results,
                 truth = isFraud,
                 estimate = .pred_class,
                 .pred_No)

# Plot roc_curve
last_fit_results %>%
  roc_curve(truth = isFraud, .pred_No) %>%
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )
```

## Feature engineering

Here I will introduce how to do feature engineering with tidymodels. Let's start
with an easy example, looking for and removing highly correlated numeric 
features.
```{r}
# Use the cor() function to find the correlated values
fraud_train %>%
  select_if(is.numeric) %>%
  cor()
```

```{r}
# Visualize the relationship in question
fraud_train %>%
  ggplot(aes(oldbalanceDest , newbalanceDest)) +
  geom_point(alpha = 0.5) +
  theme_minimal()
```

In tidymodels all feature engineering functions start with `step_*()` which makes
it super easy to explore and deal with. Below I also introduce the `prep()` and
`bake()` functions which allows us to apply the feature engineering to the data.
```{r}
# Specify a recipe object
fraud_cor_rec <- recipe(isFraud ~ ., data = fraud_train) %>% 
  # Remove correlated variables
  step_corr(all_numeric(), threshold = 0.9)

# Train the recipe
fraud_cor_rec_prep <- fraud_cor_rec %>% 
  prep(training = fraud_train)

# Apply to training data
fraud_cor_rec_prep %>% 
  bake(new_data = NULL)

# Apply to test data
fraud_cor_rec_prep %>% 
  bake(new_data = fraud_test)
```

We can take it 1 step further and apply normalization, deal with the 
non-numeric data, and then lastly deal with the class imbalance - will use the
`themis` library/package to apply SMOTE procedure for class imbalance.

If we wanted to do PCA, we can do it here by using `step_ica()`, `step_kpca()`, 
or `step_pca()`

In the next step we bring in the `themis` package within tidymodels to use the
`step_smote()` function. This will address the class balance issue we discovered
when exploring the data.

```{r}
# Load the themis package to use SMOTE (Synthetic Minority Over-​sampling 
# Technique) to deal with the class imbalance.
library(themis)

# Specify a recipe object
fraud_norm_rec <- recipe(isFraud ~ ., data = fraud_train) %>%
  # Remove correlated variables
  step_corr(all_numeric(), threshold = 0.9) %>%
  # Add log transformation step
  step_log(all_numeric(), base = 10, offset = 0.01) %>%
  # Normalize numeric predictors - do this before normalizing
  step_normalize(all_numeric()) %>%
  # Encode categorical data into numerical data
  step_dummy(all_nominal(), -all_outcomes()) %>%
  # Deal with class imbalance
  step_smote(isFraud)

# Train the recipe using the new engineered features
fraud_test_prep <- fraud_norm_rec %>%
  prep(training = fraud_train) %>%
  bake(new_data = fraud_test)

fraud_train_prep <- fraud_norm_rec %>%
  prep(training = fraud_train) %>%
  bake(new_data = NULL)

fraud_norm_rec
fraud_test_prep
fraud_train_prep
```

## Fit and predict new cleaned up (feature engineered) data

```{r}
# Train logistic model
logistic_fit <- logistic_model %>% 
  fit(isFraud ~ ., data = fraud_train_prep)

# Obtain class predictions
class_preds <- predict(logistic_fit, new_data = fraud_test_prep, type = 'class')

# Obtain estimated probabilities
prob_preds <- predict(logistic_fit, new_data = fraud_test_prep, type = 'prob')

# Combine test set results
fraud_results <- fraud_test_prep %>% 
  select(isFraud) %>% 
  bind_cols(class_preds, prob_preds)

fraud_results
```

## Evaluate the model with feature engineered data

```{r}
# Confusion matrix results
fraud_results %>%
  conf_mat(truth = isFraud, estimate = .pred_class)

# Plot the ROC curve
fraud_results %>%
  roc_curve(truth = isFraud, estimate = .pred_No) %>%
  autoplot()  +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )
```

# Modeling V2

We are going to switch models here and use a decision tree as opposed to 
logistic regression. Instead of having to redo everything we went through above
we will begin putting together a `workflow()`. Workflows are "ML pipeline" in
the tidymodels world.

To create the workflow we will add a model and a recipe. In this case we will
add the decision tree model and then the feature engineered recipe we did above.
After that we can apply the split data to the workflow and get results.

```{r}
# Choose model, engine, mode - decision tree
dt_model <- decision_tree() %>%
  # Specify the engine
  set_engine("rpart") %>%
  # Specify the mode
  set_mode("classification")

# Create a workflow - combine model and recipe
fraud_dt_wkfl <- workflow() %>%
  # Include the model object
  add_model(dt_model) %>%
  # Include the recipe object we created above
  add_recipe(fraud_norm_rec)

# Finish up by training the workflow
fraud_dt_wkfl_fit <- fraud_dt_wkfl %>%
  last_fit(split = fraud_split)

# Calculate performance metrics on test data
fraud_dt_wkfl_fit %>%
  collect_metrics()
```

Having the `workflow()` helps us better keep track of things!

## Validation folds 
Up until now we have used a single train/test split. We can help our models 
less likely to be influenced by outliers and subsequently overfitting the 
data by using validation folds.

The rsample package within tidymodels has the `vfold_cv()` function to do just 
that.

```{r}
# Create cross validation folds
set.seed(456)
fraud_folds <- vfold_cv(fraud_train, v = 10, strata = isFraud)

# Print out the folds
fraud_folds

# Obtain metrics for our folds
fraud_metrics <- metric_set(roc_auc, sens, spec)

# Now we train a model for every fold
fraud_dt_rs <- fraud_dt_wkfl %>%
  fit_resamples(resamples = fraud_folds, metrics = fraud_metrics)

# And measure the out of sample performance for each
fraud_dt_rs %>% collect_metrics()
```

We can use everything we've put together and done up until now in a more 
cohesive single chunk of code so you can see things running together and in 
order.

This is closer to looking like what you may typically see in a machine learning
model project.
```{r}
# I have left out the train/test split and feature engineering stuff but that
# would go here before the workflow stuff.

# Create decision tree workflow - combine model and recipe
fraud_dt_wkfl <- workflow() %>%
  # Include the model object
  add_model(dt_model) %>%
  # Include the recipe object
  add_recipe(fraud_norm_rec)

# Create logistic regression workflow - combine model and recipe
fraud_logistic_wkfl <- workflow() %>%
  # Include the model object
  add_model(logistic_model) %>%
  # Include the recipe object
  add_recipe(fraud_norm_rec)

# Fit Resamples - create cross validation folds and metrics
fraud_folds <- vfold_cv(fraud_train, v = 10, strata = isFraud)
fraud_metrics <- metric_set(roc_auc, sens, spec)

fraud_dt_rs <- fraud_dt_wkfl %>%
  fit_resamples(resamples = fraud_folds, metrics = fraud_metrics)
fraud_logistic_rs <- fraud_logistic_wkfl %>% 
  fit_resamples(resamples = fraud_folds, metrics = fraud_metrics)

fraud_dt_rs %>% 
  collect_metrics()
fraud_logistic_rs %>% 
  collect_metrics()

# Compare model performance
# Detailed cross validation results
dt_rs_results <- fraud_dt_rs %>% 
  collect_metrics(summarize = FALSE)
logistic_rs_results <- fraud_logistic_rs %>%
  collect_metrics(summarize = FALSE)

# Explore model performance for decision tree
dt_rs_results %>% 
  group_by(.metric) %>% 
  summarize(min = min(.estimate, na.rm = TRUE),
            median = median(.estimate, na.rm = TRUE),
            max = max(.estimate, na.rm = TRUE))

# Explore model performance for logistic regression
logistic_rs_results %>% 
  group_by(.metric) %>% 
  summarize(min = min(.estimate, na.rm = TRUE),
            median = median(.estimate, na.rm = TRUE),
            max = max(.estimate, na.rm = TRUE))
```

## Hyperparameters tuning

The last thing I want to cover is hyperparameter tuning. We can use the `tune()`
function from the `tune` package within tidymodels to do just that.

The default values set by the `parsnip` model in tidymodels for decision trees
is `min_n = 20`, `tree_depth = 30`, and `cost_complexity = 0.01`. min_n is the
minimum bumber of samples required to split a node, tree_depth is the 
maximum allowed depth of the tree, and cost_complexity is the penalty for the 
tree complexity. 
```{r}
# Set hyperparameters for tuning in the model specification step
dt_tune_model <- decision_tree(
  cost_complexity = tune(), tree_depth = tune(), min_n = tune()
  ) %>% 
  # Specify engine
  set_engine('rpart') %>% 
  # Specify mode
  set_mode('classification')

# Crete a tuning workflow
fraud_dt_tune_wkfl <- fraud_dt_wkfl %>%
  # Replace model
  update_model(dt_tune_model)

# Hyperparameter tuning with grid search
set.seed(214)
dt_grid <- grid_random(parameters(dt_tune_model), size = 5)

dt_grid

# Hyperparameter tuning
dt_tuning <- fraud_dt_tune_wkfl %>% 
  tune_grid(
    resamples = fraud_folds,
    grid = dt_grid,
    metrics = fraud_metrics
    )
```

```{r}
# View results
autoplot(dt_tuning)

dt_tuning %>% 
  collect_metrics()

dt_tuning %>%
  collect_metrics(summarize = FALSE)
```

Pick the best one!

```{r}
# Collect detailed tuning results
dt_tuning_results <- dt_tuning %>% 
  collect_metrics(summarize = FALSE)

# Explore detailed ROC AUC results for each fold
dt_tuning_results %>% 
  filter(.metric == 'roc_auc') %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median((.estimate)),
            max_roc_auc = max((.estimate)))

# Display 5 best performing models
dt_tuning %>% 
  show_best(metric = 'roc_auc', n = 5)

# Select based on best performance
best_dt_model <- dt_tuning %>% 
  # Choose the best model based on roc_auc
  select_best(metric = 'roc_auc')

# Finalize your workflow
final_fraud_wkfl <- fraud_dt_tune_wkfl %>% 
  finalize_workflow(best_dt_model)

final_fraud_wkfl
```

At this point if you wanted to combine models you could do so via the `stacks`
package within tidymodels! I will not cover that here.

Almost done - the final train
```{r}
# Train finalized decision tree workflow
fraud_final_fit <- final_fraud_wkfl %>% 
  last_fit(split = fraud_split)

# View performance metrics
fraud_final_fit %>% 
  collect_metrics()

# Create an ROC curve
fraud_final_fit %>% 
  # Collect predictions
  collect_predictions() %>%
  # Calculate ROC curve metrics
  roc_curve(truth = isFraud, .pred_No) %>%
  # Plot the ROC curve
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classied)"
  )
```

# Bonus!!! Export the model to use in production!!

If you are satisfied with the model you created and are ready to add it to a
wonderful Shiny app you created you would do so by exporting the workflow!

A word of caution, modeling pipelines can take up A LOT OF MEMORY. Guess what?
Tidymodels can help you here too! You can use the `butcher` package within 
tidymodels to "axe parts of the fitted output that are no longer needed, without 
sacrificing much functionality from the original model object"
```{r}
# Extract the workflow object to make predictions with
fraud_wf_model <- fraud_final_fit$.workflow

# Save the model to be used later
saveRDS(fraud_wf_model, "./fraud_wf_model.rds")

# Lets also save the metrics so that we can see how the model performs on new
# Data coming through our Shiny application
collect_metrics(fraud_final_fit) %>%
  write_csv("./fraud_model_metrics.csv")
```

From here you could use the `plumber` package to create an API that calls this
model and saves the results of the model to the model metrics csv!

Good luck!

If you have any questions feel free to reach out to me: alexander.r.farach@accenturefederal.com
