---
title: "Tidymodels workflow example - fraud prediction"
author: "Alex Farach"
date: "10/06/2021"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
  cache = TRUE,
  cache.lazy = TRUE,
  warning = FALSE,
  message = FALSE,
  dpi = 180,
  fig.width = 8,
  fig.height = 5,
  echo = TRUE
  )

library(tidyverse)
theme_set(theme_minimal())
```

# Typical steps in a machine learning project ----------------------------------
Adapted from the excellent "Hands-On Machine Learning with Scikit-Learn, Keras, and TensorFlow": https://www.oreilly.com/library/view/hands-on-machine-learning/9781492032632/

1. Get the data
2. Explore the data
  - Study attributes
    - name
    - types 
    - missing values
    - noisiness (stochastic, outliers, etc)
    - Usefulness
    - Distributions (uniform, logarithmic, etc.)
  - Identify the dependent variable
  - Visualize the data
  - Review correlations
3. Prep the data
  - Clean-up
    - Fix or remove outliers
    - Fill in missing values or drop them.
  - Feature selection (maybe). Drop features that provide no useful info.
  - Feature engineering (maybe). Bucketing continuous variables, add 
    transformations (log, sqrts, etc.). Create new features like recency if
    dealing with time features.
  - Feature scaling (maybe). Normalize/standardize
4. Shortlist promising models
  - Train a bunch of quick and dirty models from different categories (e.g.
    linear, naive Bayes, SVM, random forest, neural net, etc.)
  - Measure and compare performance (use validation folds)
  - Analyze results
    - Significant variables
    - Errors
  - Quick round of feature selection and engineering.
  - Repeat above steps a couple of times.
  - Pick best model/s
5. Fine-tuning
  - Hyperparameter tuning using cross-validation
  - Ensemble methods (maybe)
  - Once confident about the final model, measure performance on test set.
6. Present results (Rmarkdown/Shiny dashboard)
7. Deploy model

In the example that follows I slowly add different elements of this whole list
in order to present the tidymodels machine learning approach in a more 
digestible form.

I will introduce concepts one by one and slowly build on each topic. 
Eventually, most everything above will be covered. This is to say what follows
is not the proper way to build a machine learning model - it's the way I find 
it easiest to learn about tidymodels and machine learning pipelines generally.

Some other helpful resources:
-tidymodels.org: https://www.tidymodels.org/
-Tidy Modeling with R: https://www.tmwr.org/
-Supervised Machine Learning for Text Analysis in R: https://smltar.com/

# Tidymodels approach 
## Get the data

The following table comes from the kaggle dataset: 
  https://www.kaggle.com/ntnu-testimon/paysim1
```{r load data}
# Import the data
fraud_data <- read_csv("./example_data/fraud_example.csv")

glimpse(fraud_data)
```

## Explore the data
```{r}
# Look at counts
fraud_data %>%
  group_by(isFraud) %>%
  summarise(
    n = n()
  ) %>%
  ungroup()

# Get percentages
fraud_data %>%
  count(isFraud) %>%
  mutate(per_n = scales::percent(n/sum(n), accuracy = 0.01))
```

## Format the data
```{r clean data}
library(tidymodels)

# Clean data a bit
fraud_model_data <-
  fraud_data %>%
  select(
    isFraud, step, type, amount, oldbalanceOrg, newbalanceOrig, oldbalanceDest,
    newbalanceDest
  ) %>%
  mutate(
    isFraud = as.factor(ifelse(isFraud == 1, 0, 1))
  ) %>%
  mutate_if(is.character, as.factor)

# Set seed for reproducibility
set.seed(2021)
# sample the data
fraud_model_data <- fraud_model_data %>%
  sample_frac(0.03)

# Get percentages
fraud_model_data %>%
  count(isFraud) %>%
  mutate(per_n = scales::percent(n/sum(n), accuracy = 0.01))
```
## Create split, train, and test datasets

Here we are just creating a training and testing split. If you wanted to you
could split the training data further to get a validation set using the `mc_cv()`
function in the `rsample` package. This is a good practice but for the sake of 
simplicity I am omitting here.

It's also a good practice to split the data earlier so that steps taken in the
cleaning part of the machine learning process could be replicated in a ML
pipeline.

```{r set up train/test}
# Set seed for reproducibility
set.seed(2021)

# Create initial split
fraud_split <- initial_split(fraud_model_data, prop = 0.75, strata = isFraud)

# Assign the trainging set
fraud_train <- training(fraud_split)

# Assign the test set
fraud_test <- testing(fraud_split)

# Print out the size of training and testing sets
print(paste("Size of training data:", nrow(fraud_train)))
print(paste("Size of testing data:", nrow(fraud_test)))
```
# Modeling V1
Ideally you would want to use more than 2 models but here I will just present
2 for the sake of simplicity: a logistic model and a decision tree model. Both
will work for our binary (fraud/not fraud) model. For a multiclass 
classification problem we could do xgboost or ranger random forests. If we were
doing text classification models we could look to a regularized regression model.

There are A LOT of options depending on the problem. Here is a useful cheat 
sheet for figuring out which machine learning algorithm to use:
"https://blogs.sas.com/content/subconsciousmusings/2020/12/09/machine-learning-algorithm-use/#prettyPhoto/0/"

If you would like to see all the models in Tidymodels you can do so by going to
this link: "https://www.tidymodels.org/find/parsnip/"

## Specify the model - simple logistic regression
```{r specify_lg_simple}
# Specify a logistic regression model
logistic_model <- logistic_reg() %>% 
  # Set the engine
  set_engine('glm') %>% 
  # Set the mode
  set_mode('classification')

# Print the model specification
logistic_model
```

## Fit the model to the training data
```{r fit_lg_simple}
# Fit to training data
logistic_fit <- logistic_model %>% 
  fit(isFraud ~ ., data = fraud_train)

# Print model fit object
logistic_fit
```

## Combine test dataset results
```{r combine_lg_simple_pred}
# Predict outcome categories
class_preds <- predict(logistic_fit, new_data = fraud_test,
                       type = 'class')

# Obtain estimated probabilities for each outcome value
prob_preds <- predict(logistic_fit, new_data = fraud_test,
                       type = 'prob')

# Combine test set results
fraud_results <- fraud_test %>% 
  select(isFraud) %>% 
  bind_cols(class_preds, prob_preds)

# View results tibble
fraud_results
```

## Evaluate performance
```{r evaluate_lg_simple}
# Create custom metric set to evaluate performance.
custom_metrics <- metric_set(accuracy, sens, spec, precision, recall, f_meas)

# Print out the custom metrics results
custom_metrics(fraud_results, truth = isFraud, estimate = .pred_class)

# Here are all the available metrics
conf_mat(fraud_results, truth = isFraud, estimate = .pred_class) %>%
  summary()
```

## Detour to talk about performance metrics

Which performance metric you decide to optimize has implications for which model
you want to use and how to tune said chosen model. It's worthwhile to do a quick
review of them.

The following was adapted from this excellent post by S.Ghoneim:
https://towardsdatascience.com/accuracy-recall-precision-f-score-specificity-which-to-optimize-on-867d3f11124

### Accuracy
The ratio of the correctly labeled subjects to the whole pool of subjects.

Accuracy = (TP+TN)/(TP+FP+FN+TN)

How many fraudsters did we correctly label out of all the fraudsters?

```{r}
accuracy(fraud_results, truth = isFraud, estimate = .pred_class)
```

### Precision
The ratio of the correctly positive labeled by our program to all positive 
labeled.

Precision = TP/(TP+FP)

How many of those who we labeled as fraudsters are actually fraudsters?

```{r}
precision(fraud_results, truth = isFraud, estimate = .pred_class)
```

### Recall (aka Sensitivity)
Recall is the ratio of the correctly positive labeled by our program to all who 
are fraudulent in reality.

Recall = TP/(TP+FN)

Of all the transactions that are fraudulent, how many of those we correctly 
predict?

```{r}
recall(fraud_results, truth = isFraud, estimate = .pred_class)
```

### Specificity
Specificity is the correctly -ve labeled by the program to all who are healthy 
in reality.

Specificity = TN/(TN+FP)

Of all the legitimate transactions, how many of those did we correctly predict?

```{r}
specificity(fraud_results, truth = isFraud, estimate = .pred_class)
```

### F1-score (aka F-Score / F-Measure)

F1 Score considers both precision and recall.
It is the harmonic mean(average) of the precision and recall.

F1 Score = 2*(Recall * Precision) / (Recall + Precision)

F1 Score is best if there is some sort of balance between precision (p) & recall 
(r) in the system. Oppositely F1 Score isn’t so high if one measure is improved 
at the expense of the other.
```{r}
f_meas(fraud_results, truth = isFraud, estimate = .pred_class)
```

So which should we choose? In this case we want to optimize recall and the 
f-measure.

A focus on recall because we would rather get some extra false positives over
saving some false negatives. We would rather label some legitimate transactions
as fraudulent over missing actual, real fraudulent transactions.

The f-measure takes into consideration recall but also considers precision. This
is helpful because we have an uneven class distribution. Precision is how sure
we are of our true positives. Recall is how sure we are that we are not
missing any positives.

## Visual evaluation - confusion matrix, ROC curve and area under ROC curve
```{r eval_lg_simple_viz}
# Create confusion matrix to see TP, FP, TN, and FN results
fraud_results %>%
  conf_mat(truth = isFraud, estimate = .pred_class) %>%
  autoplot('heatmap')

# Plot roc_curve
fraud_results %>%
  roc_curve(truth = isFraud, estimate = .pred_0) %>%
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )

# Print out the AUC of the ROC curve
roc_auc(fraud_results, truth = isFraud, .pred_0)
```

## Complete the model training process

Our approach thus far has been really simple. We only used a single training 
set. Later on I'll show you how to use validation folds and I mentioned the use 
of a validation set above which would add some complications to these first 
model training steps.

Let's say we were happy here though. The last fit will fit the best model to the 
training set and evaluate on the test set which is why we pass the fraud_split 
data to the function and not just the training or the testing set.

```{r lg_simple_wf}
# Train model with last fit
fraud_last_fit <- logistic_model %>%
  last_fit(isFraud ~ ., split = fraud_split)

# Collect predictions
last_fit_results <- fraud_last_fit %>%
  collect_predictions()

# Custom metrics function
last_fit_metrics <- metric_set(accuracy, sens, spec, precision, recall, f_meas)

# Calculate metrics
last_fit_metrics(last_fit_results,
                 truth = isFraud,
                 estimate = .pred_class,
                 .pred_0)

# Plot roc_curve
last_fit_results %>%
  roc_curve(truth = isFraud, .pred_0) %>%
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )
```

## Feature engineering

Here I will introduce how to do feature engineering with tidymodels. Let's start
with an easy example, looking for and removing highly correlated numeric 
features.
```{r find correlations}
# Use the cor() function to find the correlated values
fraud_train %>%
  select_if(is.numeric) %>%
  cor()
```

```{r visualize correlations}
# Visualize the relationship in question
fraud_train %>%
  ggplot(aes(oldbalanceDest , newbalanceDest)) +
  geom_point(alpha = 0.5) +
  theme_minimal()
```

In tidymodels all feature engineering functions start with `step_*()` which makes
it super easy to explore and deal with. Below I also introduce the `prep()` and
`bake()` functions which allows us to apply the feature engineering to the data.
```{r first pass at feature engineering}
# Specify a recipe object
fraud_cor_rec <- recipe(isFraud ~ ., data = fraud_train) %>% 
  # Remove correlated variables
  step_corr(all_numeric(), threshold = 0.9)

# Train the recipe
fraud_cor_rec_prep <- fraud_cor_rec %>% 
  prep(training = fraud_train)

# Apply to training data
fraud_cor_rec_prep %>% 
  bake(new_data = NULL)

# Apply to test data
fraud_cor_rec_prep %>% 
  bake(new_data = fraud_test)
```

We can take it 1 step further and apply normalization, deal with the 
non-numeric data, and then lastly deal with the class imbalance - will use the
`themis` library/package to apply SMOTE procedure for class imbalance.

If we wanted to do PCA, we can do it here by using `step_ica()`, `step_kpca()`, 
or `step_pca()`

In the next step we bring in the `themis` package within tidymodels to use the
`step_smote()` function. This will address the class balance issue we discovered
when exploring the data.

The `recipes` package is extensive. Please see the documentation for the full
breadth of the recipes it has available. If you want to create your own recipe 
instructions to do so are here: https://recipes.tidymodels.org/reference/recipe.html

```{r second pass at feature engineering}
# Load the themis package to use SMOTE (Synthetic Minority Over-​sampling 
# Technique). This package has add-on steps to deal with class imbalance.
library(themis)

# Specify a recipe object
fraud_norm_rec <- recipe(isFraud ~ ., data = fraud_train) %>%
  # Remove correlated variables
  step_corr(all_numeric(), threshold = 0.9) %>%
  # Add log transformation step
  step_log(all_numeric(), base = 10, offset = 0.01) %>%
  # Normalize numeric predictors
  step_normalize(all_numeric()) %>%
  # Encode categorical data into numerical data
  step_dummy(all_nominal(), -all_outcomes()) %>%
  # Deal with class imbalance
  step_smote(isFraud)

# Train the recipe using the new engineered features
fraud_test_prep <- fraud_norm_rec %>%
  prep(training = fraud_train) %>%
  bake(new_data = fraud_test)

fraud_train_prep <- fraud_norm_rec %>%
  prep(training = fraud_train) %>%
  bake(new_data = NULL)

fraud_norm_rec
fraud_test_prep
fraud_train_prep
```

## Fit and predict new cleaned up (feature engineered) data

```{r fit ft eng logistic model}
# Train logistic model
logistic_fit <- logistic_model %>% 
  fit(isFraud ~ ., data = fraud_train_prep)

# Obtain class predictions
class_preds <- predict(logistic_fit, new_data = fraud_test_prep, type = 'class')

# Obtain estimated probabilities
prob_preds <- predict(logistic_fit, new_data = fraud_test_prep, type = 'prob')

# Combine test set results
fraud_results <- fraud_test_prep %>% 
  select(isFraud) %>% 
  bind_cols(class_preds, prob_preds)

fraud_results
```

## Evaluate the model with feature engineered data

Here is when the performance metric we want to optimize really matters. Prior to
all the feature engineering, when we used that very basic logistic regression 
model our false negatives were 33 and now they are 3,714! Our recall improved
but our f1 score suffered since our precision suffered.

Our true positives went from 25 to 82 though! This becomes a business decision.
Since these are fraudulent transactions we need to think about the difference
between these 2 numbers.

What happens when we suspect a fraudulent transaction? What happens when we miss 
an actual fraudulent transaction? What costs more, dealing with the fallout
from cancelling a real transaction or dealing with the fallout of missing a real
fraud event?

Performance metrics matter.

```{r evaluate performance}
# Confusion matrix results
fraud_results %>%
  conf_mat(truth = isFraud, estimate = .pred_class)

# Plot the ROC curve
fraud_results %>%
  roc_curve(truth = isFraud, estimate = .pred_0) %>%
  autoplot()  +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classfied)"
  )
```

# Modeling V2

We are going to switch models here and use a decision tree as opposed to 
logistic regression. Instead of having to redo everything we went through above
we will begin putting together a `workflow()`. Workflows are "ML pipeline" in
the tidymodels world.

To create the workflow we will add a model and a recipe. In this case we will
add the decision tree model and then the feature engineered recipe we did above.
After that we can apply the split data to the workflow and get results.

```{r create new decision tree model}
# Choose model, engine, mode - decision tree
dt_model <- decision_tree() %>%
  # Specify the engine
  set_engine("rpart") %>%
  # Specify the mode
  set_mode("classification")

# Create a workflow - combine model and recipe
fraud_dt_wkfl <- workflow() %>%
  # Include the model object
  add_model(dt_model) %>%
  # Include the recipe object we created above
  add_recipe(fraud_norm_rec)

# Finish up by training the workflow
fraud_dt_wkfl_fit <- fraud_dt_wkfl %>%
  last_fit(split = fraud_split, metrics = last_fit_metrics)

# Calculate performance metrics on test data
fraud_dt_wkfl_fit %>%
  collect_metrics()
```

Having the `workflow()` helps us better keep track of things!

## Validation folds 
Up until now we have used a single train/test split. We can help our models 
less likely to be influenced by outliers and subsequently overfitting the 
data by using validation folds.

The rsample package within tidymodels has the `vfold_cv()` function to do just 
that.

```{r apply validation folds}
# Use paralleization to improve performance
doParallel::registerDoParallel()

# Create cross validation folds
set.seed(2021)
fraud_folds <- vfold_cv(fraud_train, v = 10, strata = isFraud)

# Print out the folds
fraud_folds

# Now we train a model for every fold
fraud_dt_rs <- fraud_dt_wkfl %>%
  fit_resamples(resamples = fraud_folds, metrics = last_fit_metrics)

# And measure the out of sample performance for each
fraud_dt_rs %>% collect_metrics()
```

We can use everything we've put together and done up until now in a more 
cohesive single chunk of code so you can see things running together and in 
order.

This is closer to looking like what you may typically see in a machine learning
model project.

```{r rerun models and evaluate performance}
# I have left out the train/test split and feature engineering stuff but that
# would go here before the workflow stuff.

# Create decision tree workflow - combine model and recipe
fraud_dt_wkfl <- workflow() %>%
  # Include the model object
  add_model(dt_model) %>%
  # Include the recipe object
  add_recipe(fraud_norm_rec)

# Create logistic regression workflow - combine model and recipe
fraud_logistic_wkfl <- workflow() %>%
  # Include the model object
  add_model(logistic_model) %>%
  # Include the recipe object
  add_recipe(fraud_norm_rec)

# Fit Resamples - create cross validation folds and metrics
fraud_folds <- vfold_cv(fraud_train, v = 10, strata = isFraud)
fraud_metrics <- metric_set(accuracy, sens, spec, precision, recall, f_meas)

fraud_dt_rs <- fraud_dt_wkfl %>%
  fit_resamples(resamples = fraud_folds, metrics = last_fit_metrics)
fraud_logistic_rs <- fraud_logistic_wkfl %>% 
  fit_resamples(resamples = fraud_folds, metrics = last_fit_metrics)

fraud_dt_rs %>% 
  collect_metrics() %>%
  mutate(model = "decision_tree")
fraud_logistic_rs %>% 
  collect_metrics() %>%
  mutate(model = "logistic_regression")

# Compare model performance
# Detailed cross validation results
dt_rs_results <- fraud_dt_rs %>% 
  collect_metrics(summarize = FALSE)
logistic_rs_results <- fraud_logistic_rs %>%
  collect_metrics(summarize = FALSE)

# Explore model performance for decision tree
dt_rs_results %>% 
  group_by(.metric) %>% 
  summarize(min = min(.estimate, na.rm = TRUE),
            median = median(.estimate, na.rm = TRUE),
            max = max(.estimate, na.rm = TRUE)) %>%
  mutate(model = "decision_tree")

# Explore model performance for logistic regression
logistic_rs_results %>% 
  group_by(.metric) %>% 
  summarize(min = min(.estimate, na.rm = TRUE),
            median = median(.estimate, na.rm = TRUE),
            max = max(.estimate, na.rm = TRUE)) %>%
  mutate(model = "logistic_regression")
```

## Hyperparameters tuning

The last thing I want to cover is hyperparameter tuning. We can use the `tune()`
function from the `tune` package within tidymodels to do just that.

The default values set by the `parsnip` model in tidymodels for decision trees
is `min_n = 20`, `tree_depth = 30`, and `cost_complexity = 0.01`. min_n is the
minimum bumber of samples required to split a node, tree_depth is the 
maximum allowed depth of the tree, and cost_complexity is the penalty for the 
tree complexity.

```{r hyperparameter tuning}
# Set hyperparameters for tuning in the model specification step
dt_tune_model <- decision_tree(
  cost_complexity = tune(), tree_depth = tune(), min_n = tune()
  ) %>% 
  # Specify engine
  set_engine('rpart') %>% 
  # Specify mode
  set_mode('classification')

# Crete a tuning workflow
fraud_dt_tune_wkfl <- fraud_dt_wkfl %>%
  # Replace model
  update_model(dt_tune_model)

# Hyperparameter tuning with grid search
set.seed(2021)
dt_grid <- grid_random(parameters(dt_tune_model), size = 5)

dt_grid

# Hyperparameter tuning
dt_tuning <- fraud_dt_tune_wkfl %>% 
  tune_grid(
    resamples = fraud_folds,
    grid = dt_grid,
    metrics = fraud_metrics
    )
```

```{r view hyperparameter tuning results}
dt_tuning %>% 
  collect_metrics()

dt_tuning %>%
  collect_metrics(summarize = FALSE)

autoplot(dt_tuning) +
  geom_line(linetype = "dashed") +
  labs(
    x = "Hyperparameter values",
    y = "Performance metric score"
  )
```

Pick the best one!

```{r select best tuned model}
# Collect detailed tuning results
dt_tuning_results <- dt_tuning %>%
  collect_metrics(summarize = FALSE, metrics = metric_set(
    accuracy, sens, spec, precision, recall, f_meas
  ))

# Explore detailed ROC AUC results for each fold
dt_tuning_results %>% 
  filter(.metric == 'roc_auc') %>% 
  group_by(id) %>% 
  summarize(min_roc_auc = min(.estimate),
            median_roc_auc = median((.estimate)),
            max_roc_auc = max((.estimate)))

# Display 5 best performing models
dt_tuning %>% 
  show_best(metric = 'recall', n = 5)

# Select based on best performance. For a multiclass classification model
# you could add desc(penalty) to get a model where the penalty is taking out 
# more of the results - a simpler but effective model.
best_dt_model <- dt_tuning %>% 
  # Choose the best model based on roc_auc
  select_best(metric = 'recall')

# Finalize your workflow
final_fraud_wkfl <- fraud_dt_tune_wkfl %>% 
  finalize_workflow(best_dt_model)

final_fraud_wkfl
```

At this point if you wanted to combine models you could do so via the `stacks`
package within tidymodels! I will not cover that here.

Almost done - the final train
```{r final model train}
# Train finalized decision tree workflow
fraud_final_fit <- final_fraud_wkfl %>% 
  last_fit(split = fraud_split)

# View performance metrics
fraud_final_fit %>% 
  collect_metrics()

# Create an ROC curve
fraud_final_fit %>% 
  # Collect predictions
  collect_predictions() %>%
  # Calculate ROC curve metrics
  roc_curve(truth = isFraud, estimate = .pred_0) %>%
  # Plot the ROC curve
  autoplot() +
  labs(
    x = "1-specificity\n(proportion of false positives\namong true negatives)",
    y = "sensitivity\n(proportion of all positive cases that\nwere correctly classied)"
  )
```

# Bonus!!! Export the model to use in production!!

If you are satisfied with the model you created and are ready to add it to a
wonderful Shiny app you created you would do so by exporting the workflow!

A word of caution, modeling pipelines can take up A LOT OF MEMORY. Guess what?
Tidymodels can help you here too! You can use the `butcher` package within 
tidymodels to "axe parts of the fitted output that are no longer needed, without 
sacrificing much functionality from the original model object"

```{r extract model and performance metrics}
library(butcher)

# Extract the workflow object to make predictions with
fraud_wf_model <- extract_workflow(fraud_final_fit)
fraud_butcher_model <- butcher(fraud_wf_model)

print(paste("Original workflow size:", lobstr::obj_size(fraud_wf_model), "B"))
print(paste("Butchered workflow size", lobstr::obj_size(fraud_butcher_model), "B"))
```

We can now pass incoming data into our model to get our predictions

```{r make predictions on new data}
# lets go back and take a look at our original data
glimpse(fraud_data)

# We can select some random values to show how the extracted workflow would work
# on incoming data.
preds_res <- predict(fraud_butcher_model, sample_n(fraud_data, 1), type = "class")
preds_res$.pred_class
```

Now that we have our lean and mean model we can export the model to use in prod.

```{r}
# Save the model to be used later
saveRDS(fraud_butcher_model, "./fraud_butcher_model.rds")

# Lets also save the metrics so that we can see how the model performs on new
# Data coming through our Shiny application
collect_metrics(fraud_final_fit) %>%
  write_csv("./fraud_model_metrics.csv")
```

From here you could use the `plumber` package to create an API that calls this
model and saves the results of the model to the model metrics csv!

Plumber allows you to create APIs by merely decorating your existing R code with 
special annotations. The example below shows an example of the plumber.R file
that we would use to deploy this model.

This file defines two Plumber “endpoints.” One is hosted at the path /predict 
and makes the fraud prediction; the other is hosted at the path /metrics and 
shows the expected model metrics from the training data.

```{r api example}
## API setup

# Only keep packages you used - so not all of tidyverse and tidymodels to keep
# things small and light.
library(plumber)
library(dplyr)
library(parsnip)
library(workflows)
library(recipes)
library(themis)

## Load model + metrics
fraud_wf_model <- readRDS("./fraud_wf_model.rds")
fraud_metrics <- readr::read_csv("./fraud_model_metrics.csv")

#* @apiTitle Fraud detection model API
#* @apiDescription Fraud classification model predicting whether credit card transaction is fraud.

#* Submit credit card transaction data to get fraud/not fraud prediction
#* @serializer json
#* @parser json
#* @post /predict
function(req, res) {
  preds <- req$body
  preds_res <- predict(fraud_wf_model, preds, type = "class")
  preds_res$.pred_class
}

#* Expected model metrics from training
#* @serializer json
#* @get /metrics
function() {
  fraud_metrics
}
```

From here you need to find a place where you can host your plumber API. Here is
some information on the variety of ways you can do that: 
https://www.rplumber.io/articles/hosting.html

Good luck!

If you have any questions feel free to reach out to me: alexander.r.farach@accenturefederal.com
